### 2021-03-08 manuscript/manuscript.tex

%Introduction section
\section{Introduction}
The topic of mental workload is a widely studied phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}. A widely utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst they carry out a certain task. As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual. Workload needs to be recognized as a person-specific construct. The amount of perceived workload ushered by a given task may differ across individuals, due to how well one is able to cope with that particular task \cite{de1996measurement}. Hence, when referring to workload throughout this research, the person-specific nature of workload is acknowledged.

A commonly employed method for the assessment of workload is the well established NASA-Task Load Index questionnaire. This questionnaire inquires into the amount of perceived workload, and rests on six subjective sub-scales \cite{hart2006nasa}. This assessment is usually conducted post-experiment, which can in certain situations be considered undesirable. Consider for example an experiment in which it is aimed to assess workload of a pilot in flight. An insightful learning approach towards such an experiment would be to measure the degree of perceived workload at different phases of the flight. However, only after the flight is concluded, a measurement in the form of a questionnaire can be administrated. In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate bias. A widely recognized type of bias is the observer-bias, advocating that participants in an experiment tend to overexaggerate the treatment effect, i.e. the amount of perceived workload in our case, when having to report it post-experiment \cite{mahtani2018catalogue}.

An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs in order to classify workload. Examples of such bio-signals, hereafter referred to as "modalities", include techniques as electroencephalography, eye-tracking, galvanic skin response, functional near-infrared spectroscopy, etc. The advantage of such an approach is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}. Doing so poses the potential of yielding a rich and multifaceted classification of a mental construct such as workload. However most importantly, it is possible to train a separate model for each individual. It renders possible to cater towards the person-specific nature inherent to workload, the importance of which was pointed out by \citeA{de1996measurement}. This approach, however, comes at the cost of an increase in complexity. This resides in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a single classification outcome.

The current research builds upon research conducted by \citeA{dolmans2020perceived}, who proposed a deep-learning approach to multi-modular classification of workload. The current research differs from this previous endeavor in that it utilizes different modalities, and hence different data. In addition, the current research investigates upon the feasibility of a real-time approach. Real-time in this sense constitutes the real-time classification of workload, i.e. the classification of workload whilst the experiment takes place. Taking such an approach enables the possibility to conduct a dynamic experiment, the state of which can be altered by responding towards the classified degree of workload in real-time. Consider a simulation with the objective of educating its partakers, such as a surgical simulation for educating surgeons-in-training. The learning experience of a single session could be dramatically enhanced when the state of the experiment is catered towards the individual learning process. For example, in case it is recognized at the start of the session that a partaker has difficulty with a specific procedure, the remainder of the session can be catered towards focusing on this specific procedure. By enhancing the learning experience in this manner, the effectiveness of a single session can be improved upon dramatically, entailing a substantially more efficient learning process.

Three modalities are utilized in the current research. The first of which is the technique of electroencephalography
, hereafter referred to as "EEG". The second is the technique of galvanic skin response, hereafter referred to as "GSR". Lastly, the third technique is called photoplethysmography, hereafter referred to as "PPG". It is of importance to recognize that the objective of the current research is not to gain insight into the most optimal model design for each of these previously delineated modalities. The objective is rather to construct a framework with which real-time classification of a mental construct such as workload can be managed, and to which modalities of choice can easily be added in future research endeavors. Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity. Modularity refers to the extent to which different modalities can freely be added and/or removed towards the framework, without the necessity of re-architecting and rebuilding it entirely. The second design principle is the principle of generalizability, prescribing that the framework should not merely be utilizable for the classification of workload, but for the classification of other mental constructs as well.

A deep-learning approach towards the construction of a real-time multi-modular framework is adopted. Considering the complexity and sheer size of such a deep-neural network, an important point of attention is classification speed. The challenge in real-time classification with deep-learning is often not reaching adequate performance, but rather to attain adequate speed of classification. Deep neural networks easily constitute thousands of calculations to be made simultaneously, which is even more true for a multi-modular approach such as the current. In order for real-time classification to work, classification cannot take too long, for otherwise it is not real-time anymore and the previously delineated benefit of a real-time approach dissipates. As a consequence, multiple networks are considered and contrasted in terms of performance and their ability to classify in real-time. Firstly, for each of the three modalities individually, a single-modular network is constructed. Secondly, a multi-modular network is architected combining all three modalities. Additionally, several variations on this multi-modular framework are considered and contrasted. These networks are specified to vary in size, i.e. the amount of specified neurons and filters. These networks were created in Python, by utilizing the deep/machine-learning toolbox Pytorch \cite{paszke2017automatic}

>>>>

%Introduction section
\section{Introduction}
The topic of mental workload is a widely studied phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}. A widely utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst they carry out a certain task. As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual. Workload needs to be recognized as a person-specific construct. The amount of perceived workload ushered by a given task may vary across individuals due to how well one is able to cope with that particular task \cite{de1996measurement}.

A commonly employed method for the assessment of person-specific workload is the well established NASA-Task Load Index questionnaire. This questionnaire inquires into the amount of perceived workload,  and embodies six different dimensions \cite{hart2006nasa}. Such an assessment is usually conducted post-experiment, which might in certain situations be undesirable. Consider for example an experiment in which it is aimed to assess workload of a pilot in flight. An insightful learning approach towards such an experiment would be to measure the degree of perceived workload at different phases of the flight. However, only after the flight is concluded, a measurement in the form of a questionnaire can be administrated. In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate biases, such as for example the observer-bias, which advocates that participants in an experiment tend to overexaggerate the treatment effect, i.e. the amount of perceived workload, when having to report it post-experiment \cite{mahtani2018catalogue}.

An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs to predict the degree of experienced workload. Examples of such bio-signals, hereafter referred to as "modalities", include techniques such as electroencephalography, eye-tracking, galvanic skin response, functional near-infrared spectroscopy, etc. The advantage of utilizing multiple bio-signals is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}. Doing so poses the potential of yielding a rich and multifaceted prediction of a mental construct such as workload. However most importantly, it is renders possible to train a separate model for each individual, with which can be catered towards the person-specific nature inherent to workload, the importance of which was pointed out by \citeA{de1996measurement}. This approach, however, comes at the cost of an increase in complexity. This resides in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a prediction

Three modalities are utilized in the current research. The first of which is the technique of electroencephalography
, hereafter referred to as "EEG". The second is the technique of galvanic skin response, hereafter referred to as "GSR". Lastly, the third technique is called photoplethysmography, hereafter referred to as "PPG". The objective of the current study is to construct a framework with which real-time prediction of a mental construct such as workload can be managed, and to which modalities of choice can easily be added in future research endeavors. Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity. Modularity refers to the extent to which different modalities can freely be added and/or removed towards the framework, without the necessity of re-architecting and rebuilding it entirely. The second design principle is the principle of generalizability, prescribing that the framework should not merely be utilizable for the classification of workload, but for the classification of other mental constructs as well.

A deep-learning approach towards the construction of a real-time multi-modular framework is adopted. Considering the complexity and sheer size of such a deep-neural network, an important point of attention is prediction speed. The challenge in real-time prediction with deep-learning is often not reaching adequate performance, but rather to attain adequate speed of prediction. Deep neural networks easily constitute thousands of calculations to be made simultaneously, which is even more true for a multi-modular approach such as the current. In order for real-time prediction to work, prediction cannot take too long, for otherwise it is not real-time anymore and the previously delineated benefit of a real-time approach dissipates. As a consequence, multiple networks are considered and contrasted in terms of performance and their ability to predict in real-time. Firstly, for each of the three modalities individually, a single-modular network is constructed. and assessed.  Secondly, a multi-modular network is architected combining all three modalities into one. These networks were created in Python, by utilizing the deep-learning toolbox PyTorch \cite{paszke2017automatic}
